---
title: "Vliv virtuality na výkonnost týmu"
author: "Michal Lauer"
date: "`r format(Sys.time(), format = '%d. %m. %Y')`"
output:
  html_document:
    theme: paper
    css: "assets/css/style.css"
    df_print: kable
    highlight: zenburn
    code_folding: hide
    toc: true
    toc_float: true
editor_options:
  chunk_output_type: console
knit: (function(inputFile, encoding) {
  rmarkdown::render(inputFile,
                    encoding = encoding,
                    output_dir = "output/")})
---
```{r setup, include=F}
# Environment preparation
cat("\f")
rm(list = ls())
# Clear output
if (dir.exists("output") & !isTRUE(getOption("knitr.in.progress"))) {
  unlink("output", recursive = T)
}
# RMarkdown requirements for renv
require("rmarkdown")
require("yaml")
# knitr setting
knitr::opts_chunk$set(
  fig.align = "center",
  fig.path = "output/imgs/",
  fig.width = 9,
  fig.height = 7,
  dev = c("svg", "png")
)
# # gtsummary theme
# gtsummary::set_gtsummary_theme(list(
#   "style_number-arg:big.mark" = " "
# ))
# Function for printing vector length
len  <- function(fc) length(unique(fc))
diff_abs <- function(c) abs(c[2] - c[1])
diff_rel <- function(c) round(abs(c[2] - c[1])*100, 2)
```

# Preface

Purpose of this project was to get a Data Analyst Associate certification
by DataCamp. The data is artificial and do not represent a real customer.
The owner of the assignment and the data is DataCamp.

# Introduction

PetMind is a nationwide pet product retailer in the United States. With
inflation hitting 41-year highs, the company is planning to reduce the cost of
customer retention by improving brand loyalty. The first strategy is to launch
a monthly pet box subscription in three months.

The marketing team is preparing a list of popular products for the pet box
subscription. The chief marketing officer wants to know whether the list should
only include the products being purchased more than once.

The marketing team would like to answer the following questions to help
with the decision:

> How many products are being purchased more than once? </br>
> Do the products being purchased again have better sales than others? </br>
> What products are more likely to be purchased again for different types of pets?

# Libraries

This block loads all libraries.

```{r libs, message=F, warning=F}
# Data wrangling
library(readr)
library(dplyr)
library(forcats)

# Data visualization
library(skimr)
library(ggplot2)

# Text manipulation
library(glue)
library(stringr)
library(tidytext)
```

# Data preparation

The raw data set is first inspected before any further changes are made.

```{r data_raw}
data_raw <-
  read_csv(
    file = "input/pet_sales.csv",
    col_types = cols(
      product_id = col_double(),
      product_category = col_character(),
      sales = col_character(),
      price = col_double(),
      vendor_id = col_character(),
      pet_size = col_character(),
      pet_type = col_character(),
      rating = col_double(),
      re_buy = col_double()
    )
  )

head(data_raw)
```

The data needs to be first cleaned. In the clean data, the

- *product_id* is factorized,
- *product_category* is factorized,
- *sales* is parsed to numerical column *sales_usd*,
- *price* is renamed to *price_usd*,
- *vendor_id* is factorized,
- *pet_size* is ordered and factorized,
- *pet_type* is factorized,
- *rating* is parsed as integer, and
- *re_buy* is factorized.

```{r data_unfiltered}
pet_size_levels <- c("extra_small", "small", "medium", "large", "extra_large")
data_unfiltered <- 
  data_raw |> 
  mutate(product_id       = factor(product_id),
         product_category = factor(product_category),
         sales_usd        = parse_number(sales),
         price_usd        = price,
         vendor_id        = factor(vendor_id),
         pet_size         = factor(pet_size,
                                   levels = pet_size_levels, ordered = T),
         pet_type         = factor(pet_type),
         rating           = as.integer(rating),
         re_buy           = factor(x = as.logical(re_buy),
                                   labels = c("TRUE" = "Rebought",
                                              "FALSE" = "Not rebought"))) |> 
  relocate(sales_usd, .before = sales) |> 
  select(-sales)

skim_without_charts(data_unfiltered)
```

There is `r nrow(data)` spanning across `r ncol(data)` different columns.
There are `r len(data_unfiltered$pet_size)` different **pet sizes**,
`r len(data_unfiltered$pet_type)` different **pet types**, and
`r len(data_unfiltered$product_category)` **product categories**. **Product id**
and **vendor id** is different for each product, which means that product id uniquely identifies each product and each product has exactly one vendor.
**Sales** and **price** are normally distributed.

From the assignment, only *some* pet types should be considered
```{r data}
# Considered pet types
considered_types <- c("cat", "dog", "fish", "bird")
# Data filtering
data <-
  data_unfiltered |> 
  filter(pet_type %in% considered_types) |> 
  mutate(pet_type = fct_drop(pet_type))

fct_count(data$pet_type)
```

# Pet type vs. Total sales
```{r pet-vs-total-sales}
pet_total <-
  data |> 
  group_by(pet_type) |> 
  summarise(sales_usd = sum(sales_usd)) |> 
  mutate(pet_type = fct_reorder(.f = pet_type, .x = sales_usd),
         pet_type = fct_rev(pet_type))

pet_total |> 
  ggplot(aes(x = pet_type, y = sales_usd, fill = pet_type)) +
  geom_col(show.legend = F) +
  scale_y_continuous(labels = scales::dollar_format()) +
  scale_x_discrete(limits = rev) +
  scale_fill_brewer(type = "div") +
  theme_classic() +
  labs(
    title = "Most sales are made for cats and dogs",
    x = "Pet type",
    y = "Sales ($)"
  )
```

# Business questions

## Rebought products

The first question asked by the marketing team is:

> How many products are being purchased more than once?

```{r rebougt-plot}
# Compute data set for further analysis
rbt_data <- 
  data |> 
  count(re_buy) |> 
  mutate(p = n/sum(n))
# Get p-valuye
rbt_p <- prop.test(x = rbt_data$n,
                        n = rep(nrow(data), times = 2))
# Plot data
rbt_data |> 
  ggplot(aes(color = re_buy)) +
  # Lollipop head
  geom_point(aes(x = re_buy, y = n), size = 3) +
  # Lollipop body
  geom_segment(aes(x = re_buy, xend = re_buy, y = 0, yend = n), size = 1) + 
  # Lollipop description
  geom_text(aes(x = re_buy, y = n, label = glue("{n} ({round(p*100, 2)} %)")),
            nudge_y = 20, color = "black") +
  scale_y_continuous(name = "Absolute count",
                     limits = c(0, 620),
                     breaks = seq(0, 600, by = 100),
                     expand = c(0, 0),
                     sec.axis = sec_axis(name = "Relative proportion",
                                         trans = ~ ./nrow(data),
                                         breaks = seq(0, 1, by = 0.1),
                                         labels = scales::percent_format())) +
  theme_classic() +
  theme(legend.position = "none") +
  labs(title = "Items are usually not rebought",
       subtitle = glue("Absolute difference of {diff_abs(rbt_data$n)} ",
                       "({diff_rel(rbt_data$p)} %), ",
                       "p-value: {format.pval(rbt_p$p.value)}"),
       x = "Was item rebought?",
       caption = "Michal Lauer, laumi.me")
```

From the figure above, it can be seen that 
`r filter(rbt_data, re_buy == "Rebought")$n` products
(`r round(filter(rbt_data, re_buy == "Rebought")$p*100, 2)` %) of
products are being rebought.

## Sales for rebought items

The second question that is being asked is regarding sales.

> Do the products being purchased again have better sales than others?

```{r purchased-again}
# Formatted sale means
sf <-
  data |> 
  group_by(re_buy) |> 
  summarise(mean = round(mean(sales_usd)/100, 0),
            mean = prettyNum(mean, big.mark = " "),
            mean = glue("{mean}K"))
# Sales p-value
sp <- t.test(sales_usd ~ re_buy, data = data)
# Sales plot
data |> 
  ggplot(aes(x = re_buy, y = sales_usd)) +
  geom_boxplot() +
  scale_y_continuous(labels = scales::dollar_format()) +
  theme_classic() +
  labs(
    title =
      glue("There is no significant difference between rebought and not ",
           "rebought items."),
    subtitle =
      glue("Rebought mean: {filter(sf, re_buy == 'Rebought')$mean}, ",
           "Not rebought mean: {filter(sf, re_buy == 'Not rebought')$mean}, ",
           "p-value: {format.pval(sp$p.value)}"),
    x = "Was item rebought?",
    y = "Sales",
    caption = "Michal Lauer, laumi.me"
  )
```

There is no significant difference between sales for rebought and Not rebought
items.

## Different producs for different pets

The final question asked by the marketing team is:

> What products are more likely to be purchased again for different types of
pets?

```{r more-likely-again}
mtb <-
  data |> 
  filter(re_buy == "Rebought") |> 
  count(pet_type, product_category) |> 
  mutate(product_category = reorder_within(product_category, n, pet_type),
         pet_type = str_to_title(pet_type),
         pet_type = fct_relevel(pet_type))
  
mtb |> 
  ggplot(aes(x = product_category, y = n, fill = pet_type)) +
  geom_col(show.legend = F) +
  facet_wrap(vars(pet_type), ncol = 2, scales = "free") +
  coord_flip() +
  scale_x_reordered() +
  theme_classic() +
  labs(
    title = "Most rebought products are for cats and dogs",
    subtitle = "Top 3 producs for all animals are toys, snacks, and equipment",
    x = "Product category",
    y = "Total number of sales",
    caption = "Michal Lauer, laumi.me"
  )
```
